\chapter*{Bibliography and Webography}
\addcontentsline{toc}{chapter}{Bibliography and Webography}

\noindent\textbf{Books:}
\begin{enumerate}
    \item Gamma, E., Helm, R., Johnson, R., \& Vlissides, J. (1994). \textit{Design Patterns: Elements of Reusable Object-Oriented Software}. Addison-Wesley.
    \item Fowler, M. (2002). \textit{Patterns of Enterprise Application Architecture}. Addison-Wesley.
    \item Napoli, M. L. (2020). \textit{Beginning Flutter: A Hands-On Guide to App Development}. Wiley.
    \item Windmill, E. (2020). \textit{Flutter in Action}. Manning Publications.
    \item Rossel, S. (2022). \textit{Supabase in Action}. Manning Publications.
\end{enumerate}

\vspace{0.5cm}
\noindent\textbf{Academic Papers and Conference Proceedings:}
\begin{enumerate}
    \item Nicola, L., Lazarescu, V., \& Popa, M. (2021). ``A Comparative Study of Cross-Platform Frameworks for Mobile Application Development.'' \textit{Proceedings of the IEEE International Conference on Automation, Quality and Testing, Robotics (AQTR)}, pp. 1--6. IEEE.
    \item Wu, W. (2018). ``React Native vs Flutter: Cross-Platform Mobile Application Frameworks.'' \textit{Metropolia University of Applied Sciences, Bachelor's Thesis}.
    \item Biørn-Hansen, A., Grønli, T.-M., \& Ghinea, G. (2019). ``A Survey and Taxonomy of Core Concepts and Research Challenges in Cross-Platform Mobile Development.'' \textit{ACM Computing Surveys}, 51(5), Article 108, pp. 1--34.
    \item Pusuluri, S. R. (2023). ``A Comparative Analysis of Backend-as-a-Service Platforms: Firebase vs Supabase.'' \textit{International Journal of Computer Science and Information Technologies (IJCSIT)}, 14(3), pp. 45--52.
    \item Byous, J., Gupta, S., \& Arora, C. (2022). ``Real-Time Data Synchronization Techniques for Collaborative Mobile Applications.'' \textit{Proceedings of the IEEE International Conference on Cloud Computing (CLOUD)}, pp. 312--319. IEEE.
    \item PostgreSQL Global Development Group (2024). ``Row Security Policies.'' \textit{PostgreSQL 16 Documentation}, Chapter 5.8.
    \item Rocher, P. (2003). \textit{Le processus unifié 2TUP}. Eyrolles.
\end{enumerate}

\vspace{0.5cm}
\noindent\textbf{Online Documentation (Webography):}
\begin{enumerate}
    \item Flutter Documentation: \url{https://docs.flutter.dev/} (March 2026).
    \item Supabase Reference Guide: \url{https://supabase.com/docs/} (January 2026).
    \item Dart Packages and Core Libraries: \url{https://pub.dev/} (March 2026).
    \item PostgreSQL Row Level Security Guide: \url{https://www.postgresql.org/docs/current/ddl-rowsecurity.html} (January 2026).
    \item Firebase Documentation: \url{https://firebase.google.com/docs} (March 2026).
    \item OWASP Mobile Security Testing Guide: \url{https://owasp.org/www-project-mobile-security-testing-guide/} (February 2026).
    \item Object Management Group, UML Specification: \url{https://www.omg.org/spec/UML/} (March 2026).
    \item Google Material Design 3 Guidelines: \url{https://m3.material.io/} (March 2026).
\end{enumerate}

