\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}
This graduation project involved designing and implementing the real-time application ecosystem \textbf{HMI Stars} for the consulting enterprise \textbf{HMI Stars Consulting}. This work successfully addressed a real-world requirement: improving administrative, tax, and HR exchanges between an agency and its corporate clients.

The objective of centralizing communication and ensuring the traceability of documents and employee records was fully achieved. The delivered solution comprises a cross-platform mobile application for client company managers and a responsive web platform for HMI Stars administrators. Together, these two components cover the full spectrum of daily operations: real-time messaging and document exchange, employee lifecycle management (creation, editing, archiving), daily attendance logging with exportable monthly reports, leave and absence requests, disciplinary warning templates with categorized letter dispatch, and internal notes and reminders for managerial follow-up.

On the technical side, the Flutter framework demonstrated high efficiency in cross-platform development, reducing development overhead by sharing code logic between the mobile application and the web platform through a single Dart codebase. Supabase provided a reactive and secure backend, with PostgreSQL Row Level Security (RLS) policies guaranteeing strict data isolation between client companies. The implementation of native OTP-based authentication, an interactive document scanner with perspective cropping, bilingual support (French and English), and adaptive theming (light and dark modes) further enhanced the user experience and security posture.

Key personal contributions in this project include structuring the relational data model across 15+ interconnected tables, setting up global state management using Provider, resolving complex web routing and session recovery issues, and implementing the full warning template system with dynamic PDF generation.

Nonetheless, future enhancements are planned. In the short term, we plan to implement push notifications (via Firebase Cloud Messaging) to alert client managers about document updates or urgent tasks. In the medium term, adding automated PDF payslip generation based on approved monthly attendance logs could expand HMI Stars into a full-scale payroll tool. In the long term, integrating AI-powered document classification and optical character recognition (OCR) would further streamline the document intake workflow.

This internship has been a highly valuable professional and personal experience, allowing me to strengthen my software engineering skills while addressing real-world security, deployment, and user experience constraints.
