\chapter*{General introduction}
\addcontentsline{toc}{chapter}{General Introduction}
In modern business consulting, efficient communication and seamless administrative coordination between agencies and their client companies are paramount. Prior to this project, HMI Stars Consulting relied entirely on fragmented and manual communication channels, such as email, instant messaging apps, and physical paperwork, to exchange sensitive corporate files and track employee attendance. This reliance resulted in severe operational bottlenecks: critical client documents (such as KBIS registry records or VAT declarations) were frequently misplaced in cluttered email threads, employee attendance logs lacked any central traceability, and response delays for urgent administrative requests averaged three to five business days. These issues not only increased the risk of data handling errors but also delayed billing cycles.

This graduation project directly addresses these challenges within the consulting enterprise \textbf{HMI Stars Consulting}. The goal is to design and implement \textbf{HMI Stars}, a unified, real-time application ecosystem that modernizes the client-consultant relationship. The primary objective is to centralize administrative document transmission, employee management, activity tracking, and messaging within a single, secure software platform.


To meet this need, we structured our development around a monorepo architecture utilizing the \textbf{Flutter} framework for both web and mobile frontend applications, and \textbf{Supabase} for data persistence, secure authentication, and real-time synchronization.

This report is organized into three main chapters according to the Unified Process methodology guidelines:
\begin{itemize}
\item \textbf{Chapter 1} introduces the host organization, defines the problem, analyzes the existing system, and reviews related work on business communication systems.

\item \textbf{Chapter 2} covers the system design and development, including the Inception, Elaboration, and Construction phases, with UML modeling, database design, and system architecture.

\item \textbf{Chapter 3} presents the implementation phase, focusing on system deployment, functional testing, interface demonstrations, and usability evaluation.

\end{itemize}
